Joint Satellite Distributions in the Milky Way and Andromeda

### 2017-09-25 paper/paper.tex
+1 paragraph in the paper

\begin{abstract}
We focus on the spatial distribution of bright ($M_V<-8$) satellites and
pairs of galaxies with similar masses, isolation and kinematic
configurations as the Local Group. 
\end{abstract}

@@

\section{Local Group Analogues in the Illustris Simulation}
\label{sec:NumericalSetup}

We use publicly available data from the Illustris Project 
\citep{2014MNRAS.444.1518V}. 
This suite of cosmological simulations, performed using the quasi-Lagrangian
code AREPO \citep{2010MNRAS.401..791S}, follow the coupled evolution of dark 
matter and gas and includes parametrizations to account for the effects of
gas cooling, photoionization, star formation, stellar feedback, black
hole and super massive black hole feedback.

The simulation volume is a cubic box of $75$ \Mpch\ on a side.
The cosmological parameters correspond to a $\Lambda$CDM cosmology
consistent with WMAP-9 measurements \citep{2013ApJS..208...19H}.

@@

\subsection{Sample Selection: Local Group Analogues}

@@

\begin{itemize}
\item LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's separation.
\item The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\item Each galaxy in the pair must have at least $5$ satellites
  brighter than  $M_V<-9$.
\end{itemize}

>>>>

\begin{abstract}
We quantify the joint spatial distribution of satellites around the Milky way and Andromeda.
\end{abstract}

@@

\section{Local Group Satellites in the Illustris Simulation}
\label{sec:NumericalSetup}

We use publicly available data from the Illustris Project 
\citep{2014MNRAS.444.1518V}. 
This suite of cosmological simulations, performed using the quasi-Lagrangian
code AREPO \citep{2010MNRAS.401..791S}, followed the coupled evolution of dark 
matter and gas and includes parametrizations to account for the effects of
gas cooling, photoionization, star formation, stellar feedback, black
hole and super massive black hole feedback. 
The simulation volume is a cubic box of $75$ \Mpch\ on a side.
The cosmological parameters correspond to a $\Lambda$CDM cosmology
consistent with WMAP-9 measurements \citep{2013ApJS..208...19H}.

@@

The smallest satellites are barely resolved in stellar mass at magnitudes of
$M_V=9$, however its dark matter structure is sampled with at least
$100$ particles. 
We find that all considered halos have at least $XX$ subhalos above
a maximum circular velocity of $15$\kms.
For this reason we select the satellite galaxy samples from the
DM subhalo population and not from the galaxies with photometry.
We chose in two different ways the sub-halo samples. 
First, we rank the halos by decreasing order of its maximum circular
velocity and select the first $N_p$ halos in the list.
Second, we select all satellites above maximum circular velocity of
$20$\kms to randmbly subsample $N_p$ subhalos.

@@

\begin{itemize}
\item LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's separation.
\item The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}
